Evaluation of performances

### 2020-02-25 analysis/eval-performance.Rmd
wflow_publish(knitr_in("analysis/eval-performance.Rmd"), view = FALSE, verbose = TRUE)

source(here::here("code/99-packages.R"))
load_packages()

# load drake objects
loadd(
  bm_aggregated_new_buffer2
)
library("xtable")
library("flextable")
library("ggbeeswarm")
library("ggsci")
library("ggrepel")
library("ggpubr")
```

@@

# save as latex table
table1 %>%
  ungroup() %>%
  arrange(RMSE) %>%
  slice(1:15) %>%
  xtable(
    type = "latex",
    caption = "Top 15 results for any task/learner/filter combination, sorted by performance.",
    label = "tab:perf-top-15"
  ) %>%
  print(
    file = "docs/00-manuscripts/ieee/performance-top-20.tex",
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )

saveRDS(table1, "docs/00-manuscripts/presentation/table-perf.rda")

@@

# save as latex table
table2 %>%
  xtable(
    type = "latex",
    caption = "Best performance of each learner across any task and filter method.",
    label = "tab:best-learner-perf"
  ) %>%
  print(
    file = "docs/00-manuscripts/ieee/performance-best-per-learner.tex",
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    scalebox = 0.90,
    caption.placement = "top",
    timestamp = NULL
  )

saveRDS(table2, "docs/00-manuscripts/presentation/table-best-learner-per-task.rda")

@@

```{r echo = FALSE}
copy_figures()
```

>>>>

R.utils::sourceDirectory("R")
library("drake")

# load drake objects
loadd(
  bm_aggregated_new_buffer2
)
library("xtable")
library("flextable")
library("ggbeeswarm")
library("ggsci")
library("ggrepel")
library("ggpubr")
library("here")
library("mlr")
library("dplyr")
library("forcats")
```

Last update:

```{r}
date()
```

@@

# save as latex table
table1 %>%
  ungroup() %>%
  arrange(RMSE) %>%
  slice(1:15) %>%
  xtable(
    type = "latex",
    caption = "Top 15 results for any task/learner/filter combination, sorted by performance.",
    label = "tab:perf-top-15"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/performance-top-20.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )

saveRDS(table1, here("docs/00-manuscripts/presentation/table-perf.rda"))

@@

# save as latex table
table2 %>%
  xtable(
    type = "latex",
    caption = "Best performance of each learner across any task and filter method.",
    label = "tab:best-learner-perf"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/performance-best-per-learner.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    scalebox = 0.90,
    caption.placement = "top",
    timestamp = NULL
  )

saveRDS(table2, here("docs/00-manuscripts/presentation/table-best-learner-per-task.rda"))

@@
